DSCI 445 Presentation

### 2025-12-04 Presentation DSCI445.Rmd
Created some plots and the presentation file

---
title: "DSCI 445 Presentation"
author: "Ethan Schilling"
date: "2025-12-04"
output: beamer_presentation
---

@@

## Slide 1 
```{r}
library(tidyverse)
library(knitr)
library(tidymodels)
library(dplyr)
```

```{r}
TDS_unfilt <- read_csv("RWAR_TDS.csv")
TOC_unfilt <- read_csv("RWAR_TOC.csv")

df_TDS <- TDS_unfilt %>%
  rename(date = 1, value = 2) %>%
  mutate(date = as.Date(date, format = "%d-%b-%y"))

ggplot(df_TDS, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TDS Value", title = "TDS over Time")

df_TOC <- TOC_unfilt %>% 
  rename(date = 1, value = 2) %>%
  mutate(date = as.Date(date, format = "%d-%b-%y"))

ggplot(df_TOC, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TOC Value", title = "TOC over Time")
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

>>>>

---
title: "DSCI 445 Presentation"
author: "Ethan Schilling, Joshua Tobey, Dawson Carney, Reece Carmody"
date: "2025-12-04"
output: beamer_presentation
---

@@

## Slide 1

```{r}
readRDS("TOC_plot.rds")
readRDS("TDS_plot.rds")
```
